VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper.tex
re
author

%with Fault Isolation 
\title{
VM-Centric  Snapshot Deduplication  for Converged Cloud Architectures} 
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\authorinfo{
  Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
  $^\star$University of California at Santa Barbara \\
  $^\dagger$Alibaba Inc. \\
%  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
}
  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\

>>>>

%with Fault Isolation 
\title{VM-Centric Snapshot Deduplication for Converged Cloud Architectures}
%VM-Centric  Deduplication  with Fault Isolation for Snapshot Backup in the Cloud
\authorinfo{Wei Zhang\and Daniel Agun\and Tao Yang}
           {UC Santa Barbara}
           {\{wei,dagun,tyang\}@cs.ucsb.edu}
\authorinfo{Hong Tang}
           {Alibaba Inc.}
           {hongtang@alibaba-inc.com}
\authorinfo{Rich Wolski}
           {UC Santa Barbara}
           {rich@cs.ucsb.edu}

% \authorinfo{
%   Wei Zhang$^{\star}$, Daniel Agun$^\star$, Tao Yang$^\star$, Rich Wolski$^{\star}$, and  Hong Tang$^\dagger$\\
%   $^\star$University of California at Santa Barbara \\
%   $^\dagger$Alibaba Inc. \\
% %  \{wei, dagun,tyang,rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com
% }
  %{\normalsize $^\star$University of California at Santa Barbara} \ \ {\normalsize$^\dagger$Alibaba Inc.} \\
